---
title: "Untitled"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(here)
library(lubridate)
theme_set(theme_bw())
```


```{r ETL}
buscas = read_csv(here::here("data/search_data.csv"))
```

## Visão Geral dos Dados

```{r}
buscas %>% 
    ggplot(aes(x = results)) + 
    geom_histogram(binwidth = 5) 
```


## What is our daily overall clickthrough rate? How does it vary between the groups?

```{r}
buscas %>%
    mutate(date = round_date(session_start_date, unit = "day"),
           hasClick = ifelse(num_clicks > 0, 1, 0)) %>%
    group_by(date, session_id) %>%
    summarise(hasClick = sum(hasClick)) %>% 
    group_by(date) %>%
    summarise(clickRate = sum(hasClick)/n()) %>% 
    ggplot(aes(x=date, y=clickRate)) +
    geom_line() +
    geom_point()
```

```{r}
buscas %>%
    mutate(date = round_date(session_start_date, unit = "day"),
           hasClick = ifelse(num_clicks > 0, 1, 0)) %>%
    group_by(group, date, session_id) %>%
    summarise(hasClick = sum(hasClick)) %>% 
    group_by(group, date) %>%
    summarise(clickRate = sum(hasClick)/n()) %>% 
    ggplot(aes(x=date, y=clickRate, color=group)) +
    geom_line() +
    geom_point()
```

```{r}
buscas %>%
    mutate(date = round_date(session_start_date, unit = "day"),
           hasClick = ifelse(num_clicks > 0, 1, 0)) %>%
    group_by(group, session_id, date) %>%
    summarise(clickRate = sum(hasClick)/n()) %>%
    group_by(group, date) %>%
    summarise(mean=mean(clickRate), sum = sum(clickRate)) %>%
    ggplot(aes(x=date, y=mean, color=group)) +
    geom_line() +
    geom_point()
```


## Which results do people tend to try first? How does it change day-to-day?

## What is our daily overall zero results rate? How does it vary between the groups?
```{r}
buscas %>%
    mutate(date = round_date(session_start_date, unit = "day"),
           isZero= ifelse(results > 0, 0, 1)) %>%
    group_by(date, session_id) %>%
    summarise(isZero = sum(isZero)) %>% 
    group_by(date) %>%
    summarise(zeroResults = sum(isZero)/n()) %>% 
    ggplot(aes(x=date, y=zeroResults)) +
    geom_line() +
    geom_point()
```

```{r}
buscas %>%
    mutate(date = round_date(session_start_date, unit = "day"),
           isZero= ifelse(results > 0, 0, 1)) %>%
    group_by(group, date, session_id) %>%
    summarise(isZero = sum(isZero)) %>% 
    group_by(group, date) %>%
    summarise(zeroResults = sum(isZero)/n()) %>% 
    ggplot(aes(x=date, y=zeroResults, color=group)) +
    geom_line() +
    geom_point()
```


## Let session length be approximately the time between the first event and the last event in a session. Choose a variable from the dataset and describe its relationship to session length. Visualize the relationship.

